\chapter{Product information}
%Reducing the spacing from the title
\vspace{-6em}


\section{Identification}
This paper contains user manual for \emph{iCrash} system. The system
dedicated to any person who wants to inform of a car crash crisis situation in
order to allow crisis handling. The \emph{iCrash} includes:
\begin{itemize}
  \item  \emph{iCrash Desktop} - client application that provides GUI for system
  users.
  \item Server application that holds the system operations.
  \item Database that holds the data persistance.
\end{itemize}

\section{Copyright}

Copyright iCrash LLC 2017. All rights reserved.\\
iCrash is protected by copyright law and international treaties. The software is
licensed (not sold), and its use is subject to a License Agreement. Unauthorized
use, copying or distribution of the program or any of its components may result in severe criminal or civil penalties, and will be prosecuted to the maximum extent under the law.
All trademarks and registered trademarks used in this documentation are property
of their owners:\\
Java SE Development Kit (JDK), MySQL Server, MySQL Workbench are trademarks or
registered trademarks of Oracle Corporation.\\
TeX Live are trademarks or registered trademarks of TeX user groups.\\
xindy is a trademark or registered trademark of Joachim Schrod. \\
ps2pdf  is a trademark or registered trademark of Artifex Software, Inc.\\
Scene Builder is trademark or registered trademark of Gluon Labs.\\
StarUML is a trademark or registered trademark of MKLab, Co.\\
Vagrant is a trademark or registered trademark of HashiCorp.\\


\section{Trademark notices}
iCrash and all iCrash taglines are trademarks or registered trademarks of iCrash LLC in the R.F. and/or other countries. All other third-party product and company names may be trademarks of their respective owners


\section{Restrictions}
Restrictions on copying or distributing the software and its associated
documentation.

\section{Warranties}
\begin{itemize}
  \item The system has an ability to handle requests simultaneously.
  \item The system is designed such that has an ability to handle higher
  volumes, the system provides scalability.
  \item The system's performance, operations, functionality and maintenance.
  conforms to the specification.
  \item The version of the system is the most current.
  \item The systems does not contain any disabling features, viruses,
  unidentified content, instructions to permit unauthorized access to the system.
  \item The supplier provides a customer with information regarding any failure
  of security measures and executes regular audits.
  \item The supplier has the right to grant the customer the rights of use of
  the software.
  \item The technology is a original work of iCrash LLC and does not violate the
  rights of any third party.
\end{itemize}

\section{Contractual obligations}



\section{Disclaimers}

iCrash LLC assumes no responsibility for the use of the software, conveys no
license under any patent, copyright, or mask work right to the product.
The product is not an institutional system certified and guaranteed by any
governmental entity.
The software must be used with caution.

\section{Contact}
%Information for contacting the issuing organization.
Phone numbers:\\
\\
General inquiries\\
+7 999 555 55 55\\
\\
Technical Support\\
+7 999 999 50 00\\
\\
Mailing address:\\
\\
info@icrash.com\\
\\
iCrash LLC\\
1 Universitetskaya\\
Innopolis, Russia 420500